\section{Introduction}

Social media platforms and microblogging websites are some of the most popular
online stages for people to express their views. Twitter, undeniably is one of
the leading applications in this assortment. People use Twitter to post their
real-time opinions in the form of tweets. These tweets can be analyzed and
certain inferences can be extracted. These inferences can subsequently be used
for academic and business purposes.

One of the primary reasons that make Twitter a feasible choice is the diverse
nature of the users. In this research, we intend to analyze and compare the
tweets of the war-veterans and the general public. We believe wars have an
impact on soldiers’ psychological and emotional states. We try to prove this
hypothesis by comparing their tweets to the tweets posted by the civilians.

We collect public data using Twitter API and then process and count the words
with a list of positive and negative adjectives to predict the polarity of the
tweets. Then we examine a randomly collected dataset to compare the difference
between tweets by veterans/soldiers and civilians.

(TBC due to the experiment implementation)

The remainder of the paper is organized as follows. We examine on
the literature related to the topic, with papers related to previous works on
the mental health of veterans, available databases on sentiment analysis and
previous works done on sentiment analysis on social media in Section 2. In Section 3, we
introduce our dataset and the experiment done on the dataset, with the results
we have. In Section 4, we have a deep look into the result and bring the
discussion. In Section 5 and 6, we conclude and bring up future works needed
for the topic.
